---
title: "Solar Irradiation Data on Brazil"
author: "Andre Moura Gomes da Costa"
date: "December 6, 2018"
output: ioslides_presentation
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
knitr::opts_chunk$set(cache = F)
knitr::opts_chunk$set(warning = F)
knitr::opts_chunk$set(fig.keep = T)
knitr::opts_chunk$set(message = F)
knitr::opts_chunk$set(warning = F)
```


```{r load, message=F, warning=F, echo=F, cache=F}

library(gridExtra)
library(cluster)
library(vegan)
library(clusterCrit)
library(tidyr)
library(raster)
library(lubridate)
library(ggplot2)
library(dplyr)
library(RColorBrewer)
library(kableExtra)
library(geosphere)
library(corrr)
 theme_set(theme_bw())
border<-c("-51.5_4.5","-50.5_3.5","-50.5_2.5","-49.5_1.5",
          "-49.5_0.5","-48.5_-0.5","-47.5_-0.5","-46.5_-0.5",
          "-45.5_-1.5","-44.5_-1.5","-43.5_-2.5","-42.5_-2.5",
          "-41.5_-2.5","-40.5_-2.5","-39.5_-2.5","-38.5_-3.5",
          "-37.5_-4.5","-36.5_-4.5","-35.5_-5.5","-34.5_-6.5",
          "-34.5_-7.5","-34.5_-8.5","-35.5_-9.5","-35.5_-10.5",
          "-36.5_-10.5","-37.5_-11.5","-37.5_-12.5","-38.5_-13.5",
          "-38.5_-14.5","-38.5_-15.5","-38.5_-16.5","-39.5_-17.5",
          "-39.5_-18.5","-39.5_-19.5","-40.5_-20.5","-40.5_-21.5",
          "-40.5_-22.5","-41.5_-23.5","-42.5_-23.5","-43.5_-23.5",
          "-44.5_-23.5","-45.5_-23.5","-46.5_-24.5","-47.5_-25.5",
          "-48.5_-26.5","-48.5_-27.5","-48.5_-28.5","-49.5_-29.5",
          "-50.5_-30.5","-50.5_-31.5","-51.5_-32.5","-52.5_-33.5"
)

load("/home/andre/Mestrado/Dados/out_MO_min.rdata")
load("/home/andre/Mestrado/Dados/SSs.rdata")
Ano0<-1988
Dados2 <- Out %>% 
    filter( (YEAR >=Ano0 & YEAR <= 2007) ) %>% 
    mutate(    LAT=as.numeric(as.character(LAT)),
               LON=as.numeric(as.character(LON)),
  #             GHI=GHI_seas+GHI_deseas,
               DATE = dmy(paste("01",MO,YEAR, sep='/'))) %>% 
    group_by(LON,LAT)%>% 
    mutate (
        GHI_=mean(GHI_trend),
        GHI_trendo=GHI_trend-GHI_,
#        GHI = GHI_seas+GHI_lowf+GHI_month+GHI_trend,
        kt = KT_seas+KT_lowf+KT_month+KT_trend,
        D_GHI_month = lag(kt)-kt,
        Dkt_=mean(KT_trend)
    ) %>%
    ungroup() %>%
    arrange(desc(LAT),LON) 
rm(Out)

Dados2 <- mutate(Dados2, LON = round(LON,digits=1),
                 LAT = round(LAT,digits=1)) %>% 
    unite(Lon_Lat,LON,LAT,remove = F) %>%
    filter(!(Lon_Lat %in% (border)))

plote<-Dados2%>%filter(Lon_Lat=="-37.5_-6.5")
#plote<-Dados2%>%filter(Lon_Lat=="-53.5_-10.5")


tmnho=.2


DadosSeas<-Dados2 %>% filter (YEAR == 1990)
DadosOsc <-Dados2 #%>%filter(MO==7) 
DadosMedia <- Dados2 %>% group_by(LON,LAT) %>%
    summarise(GHI_=mean(GHI_),
              Dkt_=mean(Dkt_),
              GHI_sd_lowf=sd(GHI_lowf,na.rm = T),
              GHI_sd_month=sd(GHI_month,na.rm = T),
              GHI_sd_trend=sd(GHI_trend,na.rm = T),
              GHI_sd_D_month=sd(D_GHI_month,na.rm=T),
              GHI_sd_seas=sd(GHI_seas,na.rm = T)) %>% 
    unite(Lon_Lat,LON,LAT,remove = F)

SD_SumPairs <- function (data){
    size<-dim(data)[2]

    SD<-matrix(data=NA,ncol=size,nrow = size)
        for (i in 1:size){
            for (j in 1:size){
                med1<-Brasil$GHI_[pamOsc$id.med[i]]
                med2<-Brasil$GHI_[pamOsc$id.med[j]]
                
                
                SD[i,j] <- sd(data[,i]+data[,j]) /(med1+med2)
            }
        }
    rowname<-c(1:size)
    SD<-data.frame(rowname,SD)
    colnames(SD)[2:(size+1)]<-(1:size)
    return(SD)
} 

SD_SumPairsO <- function (data){
    size<-dim(data)[2]
    SD<-matrix(data=NA,ncol=size,nrow = size)
    Ratios <- SD
    GHI_med <- SD
    for (i in 1:size){
        for (j in 1:size){
            d1<-data[,i]
            d2<-data[,j]
            med1<-Brasil$GHI_[pamOsc$id.med[i]]
            med2<-Brasil$GHI_[pamOsc$id.med[j]]
            
            f <- function(razao){
                out<-sd(razao*d1+(1-razao)*d2)/
                    (razao*med1+(1-razao)*med2)
                return(out)
            }
            
            opt<-optimize(f,interval = c(0,1))
            
            SD[i,j] <- opt$objective
            Ratios[i,j] <- opt$minimum
            GHI_med[i,j] <- Ratios[i,j]*med1+(1-Ratios[i,j])*med2
            
        }
    }
    rowname<-c(1:size)
    SD<-data.frame(rowname,SD)
    colnames(SD)[2:(size+1)]<-(1:size)
    Ratios<-data.frame(rowname,Ratios)
    colnames(Ratios)[2:(size+1)]<-(1:size)
    GHI_med<-data.frame(rowname,GHI_med)
    colnames(GHI_med)[2:(size+1)]<-(1:size)
    return(list("SD"=SD,"Ratios"=Ratios,"GHI_med"=GHI_med))
} 



CorrLocal <- function(Correlacao.Tidy, faixa){
    # Correlacao Tidy must be a Data Frame for which there Codigo.x and Codigo.y.
    # Forces all elements to exist. There could be other ways to do so.
        Correlacao.aux <- Correlacao.Tidy
        Correlacao.aux <- Correlacao.aux %>%
                mutate(Codigo.x = Correlacao.Tidy$Codigo.y,
                       Codigo.y = Correlacao.Tidy$Codigo.x) %>%
                rbind(Correlacao.Tidy)
        
        Saida <- Correlacao.aux %>%
                filter(Distancia >= faixa[1] & Distancia <= faixa[2]) %>%
                group_by(Codigo.x) %>%
                summarise(cor = mean(cor, na.rm=T)) %>%
                separate(Codigo.x,c("LON","LAT"),"_")
        
        
        Saida <- mutate(Saida,
                #        MO = (ifelse(MO==0,13,MO)),
                        LON = as.numeric(as.character(LON)),
                        LAT = as.numeric(as.character(LAT)))
        return(Saida)
}


```


```{r data, message=F, warning=F, echo=F}
set.seed(30213)
Variavel = "GHI_seas"
DadosEspalhadosSeas <- DadosSeas %>% dplyr::select(LAT,LON,DATE,Variavel)%>%
    spread(DATE,Variavel) %>% 
    arrange(desc(LAT),LON) 

dataSeas<-DadosEspalhadosSeas[,-c(2,1)]

set.seed(1562)
Variavel="GHI_lowf"
DadosEspalhadosLowf <- DadosOsc %>% dplyr::filter(!is.na(GHI_lowf)) %>%
    dplyr::select(LAT,LON,DATE,Variavel)%>%
    spread(DATE,Variavel) %>% 
    arrange(desc(LAT),LON)

dataLowf<-DadosEspalhadosLowf[,-c(2,1)]

set.seed(1562)
Variavel="GHI_month"
DadosEspalhadosMonth <- DadosOsc %>% dplyr::filter(!is.na(GHI_month)) %>%
    dplyr::select(LAT,LON,DATE,Variavel)%>%
    spread(DATE,Variavel) %>% 
    arrange(desc(LAT),LON)

dataMonth<-DadosEspalhadosMonth[,-c(2,1)]

Variavel="D_GHI_month"
DadosEspalhadosDelta <- DadosOsc %>% dplyr::filter(!is.na(D_GHI_month)) %>%
    dplyr::select(LAT,LON,DATE,Variavel)%>%
    spread(DATE,Variavel) %>% 
    arrange(desc(LAT),LON)

dataDelta<-DadosEspalhadosDelta[,-c(2,1)]


set.seed(30213)
Variavel="GHI_trendo"
DadosEspalhadosTrend <- DadosOsc %>% dplyr::select(LAT,LON,DATE,Variavel)%>%
    spread(DATE,Variavel) %>% 
    arrange(desc(LAT),LON) 

#DadosM.Espalhados.S [,c(2,1)]<-DadosM.Espalhados.S[,c(2,1)]*0.00001
dataTrend<-DadosEspalhadosTrend[,-c(2,1)]

Brasil<-DadosEspalhadosTrend[,c(2,1)]
Brasil <- mutate(Brasil, LON = round(LON,digits=1),
                 LAT = round(LAT,digits=1))
Brasil <- unite(Brasil,Lon_Lat,LON,LAT,remove = F) %>% left_join(DadosMedia)

dataOsc <- dataMonth + dataLowf

```

## About this web page

This web page was made for a homework on Coursera's MOOC course: Developing Data Products, from Jhon Hopkins University. 

The next slide shows the long-term daily irradiation data for the Brazilian area in an interactive plot. It uses data from the POWER project from NASA.


## Brazil's Solar Resource Avaibility

Brazil presents high levels of solar irradiation incidence over its entire area. 

```{r mapas0, echo=FALSE}
library(plotly)

mapa<-ggplot(data=Brasil) +
        geom_raster(data=Brasil,aes(x=LON,y=LAT,fill=GHI_))+
            scale_fill_gradientn(colours = rev(c(RColorBrewer::brewer.pal(n = 8, name = "Spectral"))),  na.value = rgb(0,0,0,0))+#, limits = c(3.9,6.5)) + 
 #   geom_text(aes(x=LON,y=LAT,label=Centros),check_overlap = T, size=2)+
        coord_equal() +theme_bw()
#mapa 

ggplotly(mapa)
```

## Thanks

